\documentclass{resume}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/jfmyers9}{\Large James F. Myers Jr.}} & Email : \href{mailto:jfmyers9@gmail.com}{jfmyers9@gmail.com}\\
  \href{https://github.com/jfmyers9}{https://github.com/jfmyers9} & Mobile : +1-949-292-0504 \\
\end{tabular*}

\section{Experience}

\begin{itemize}[leftmargin=*]
	\vspace{-1pt}\item
			\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
				\textbf{Pivotal Software} & San Francisco, CA \\
				\textit{\small Senior Software Engineer} & \textit{\small January 2014 -- Present} \\
			\end{tabular*}\vspace{-5pt}

  \begin{itemize}
		\item \textbf{Diego}{: An open source distributed system for container orchestration that is used as the core runtime to Cloud Foundry.
      I worked on this project for over two years, with one year as the team lead.
      I helped the project reach it's first major version, become stable in production environments, and scale to manage over a quarter of a million containers.
      The project is mainly implemented in Golang. \vspace{-2pt}}
		\item \textbf{Cloud Foundry Runtime}{: An open source project that dealt with the core components to Cloud Foundry.
      This included distributed container orchestration, user facing API design and implementation, and distributed routing and service discovery.
      I worked on this team for over a year and worked to increase the platforms stability and add a large number of user facing features.
      The project is mainly implemented in Ruby and Golang. \vspace{-2pt}}
		\item \textbf{Security}{: A project focused on providing other Cloud Foundry teams with the ability to build and operate secure software.
			I worked on this project for six months with four of those as the team lead.
			I worked extensively on the product direction and implementation of the BOSH process manager which uses runc to execute processes in secure containers.
      The project is mainly implemented in Golang. \vspace{-2pt}}
		\item \textbf{Cloud Foundry Frontend}{: A project focused on providing a web interface to Pivotal Cloud Foundry and Pivotal Web Services.
			I worked on this project for four months.
			I worked extensively on transitioning the project to a new Javascript library as well as helping finish a user interface re-design.
      The project is mainly implemented in Ruby and Javascript. \vspace{-2pt}}
  \end{itemize}

	\vspace{-1pt}\item
			\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
				\textbf{Pivotal Labs} & San Francisco, CA \\
				\textit{\small Software Engineering Intern} & \textit{\small May 2013 -- August 2013} \\
			\end{tabular*}\vspace{-5pt}

  \begin{itemize}
		\item \textbf{Greenplum Chorus}{: A web interface to various database systems with added collaborative features to facilitate data sharing amongst organizations.
			I worked on the backend and frontend of the application which was mainly implemented in Ruby on Rails and backbone.js.
      I got extensive experience using various datasources such as Greenplum DB, Oracle DB, Hadoop, and HAWQ.
      I worked as a consultant and worked to teach agile programming to the client as well as continuous integration. \vspace{-2pt}}
  \end{itemize}
\end{itemize}

\section{Education}
\begin{itemize}[leftmargin=*]
	\vspace{-1pt}\item
			\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
				\textbf{University of California, Berkeley} & Berkeley, CA \\
				\textit{\small College of Engineering, B.S. Electrical Engineering and Computer Science} & \textit{\small August 2010 -- December 2013} \\
			\end{tabular*}\vspace{-5pt}

  \begin{itemize}
    \item Focused my studies on computer science with some background in electrical engineering
    \item Courses taken include: Articial Intelligence, Operating Systems, Programming Languages and Compilers,
					Advanced Algorithms, Computability and Complexity, Database Management Systems, Introduction to
					Communication Networks, and Computer Security
  \end{itemize}
\end{itemize}

\section{Programming Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages}{: Golang, Ruby on Rails, Javascript, Java, Python, Scheme, C, Android SDK, HTML/CSS}
  \item \textbf{Technologies}{: Continuous Integration, Runc, Docker, Kubernetes, AWS, GCP, Unix Systems, BOSH}
\end{itemize}

\end{document}
